Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
previous removed from paper

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).  When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
\end{rem}

We now restrict our attention to log canonical rings of stacky curves.  The previous lemma accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.  We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.

@@

One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.  Instead we turn now to inductive methods to incrementally increase the $e_i$s.  Combined with the previous lemmas on adding points, these will provide all the necessary inductive tools for the remainder of the paper.

>>>>

To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i P_i}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).  When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
\end{rem}

We now restrict our attention to log canonical rings of stacky curves.  Lemma \ref{lem:sat-1} accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.  We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.

@@

One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.  Instead we turn now to inductive methods to incrementally increase the $e_i$s.  Combined with the adding points lemmas, these will provide all the necessary inductive tools for the remainder of the paper.
